Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-27 doc/main_jfm.tex
starting sec 5

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of 
Janus-vesicles under a number of flows. To extract physical quantities of the target structure using the
proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm which is set as the diameter of each 
Janus particle. The force is scaled from the interfacial tension $\gamma=4.11$ pN nm$^{-1}$ 
from ~\cite{Ryham16}. This also means that the energy unit is scaled by $1\ k_BT$. We then be able to
calculate the characteristic time scale $\tau = \mu l/\gamma = 0.61$ ns where the fluid viscosity $\mu=1$ cP.
With the same framework, \cite{Fu20} provides the bending rigidity $\kappa=8.51$ $k_BT$.
%
For the model parameters, the decay length of attraction $\rho = 2l = 5$ nm, the repulsion length scale is 
$\rho_0=0.5$, and the repulsion strength $M=4.0\ k_BT$.
The dimensionless shear rate is given by $\chi = \dot\gamma \tau$ where $\dot\gamma$ is the shear rate.

>>>>

Following the relaxation experiments we consider the behavior of
Janus-vesicles under various flows. To extract physical quantities of
the target structure, we introduce the following scaling laws and the
dimensionless units. The length unit is scaled by the length of
phospholipids $l=2.5$~nm which is the diameter of each Janus particle.
The force is scaled by the interfacial tension $\gamma=4.11$~pN
nm$^{-1}$ from~\cite{Ryham16}. This means that the energy unit is scaled
by $1\ k_BT$. We can then define the characteristic time scale $\tau =
\mu l/\gamma = 0.61$~ns where the fluid viscosity is $\mu=1$ cP.  With
the same framework,~\cite{Fu20} provide the bending rigidity
$\kappa=8.51$~$k_BT$. For the model parameters, the decay length of
attraction is $\rho = 2l = 5$~nm, the repulsion length scale is
$\rho_0=0.5$, and the repulsion strength is $M=4.0$~$k_BT$. Finally, the
dimensionless shear rate is $\chi = \dot\gamma \tau$ where $\dot\gamma$
is the shear rate.
